---
title: "Time Series--Introduction"
output: html_document
---

Reference book:  [R in Action](https://www.manning.com/books/r-in-action)  
For further study, the following books are recommended:   

- [Time Series](http://www.openuniversity.edu/courses/modules/m249?): A tutorial book  
- [A Little Book of R for Time Series](http://mng.bz/8fz0): Another tutorial book with R code  
- [Forecast: Principles and Practice](http://otexts.com/fpp): Highly recommended  
  
### 生成时序对象

```{r}
sales=c(18, 33, 41, 7, 34, 35, 24, 25, 24, 21, 25, 20, 
        22, 31, 40, 29, 25, 21, 22, 54, 31, 25, 26, 35)
tsales=ts(sales, start=c(2003, 1), frequency=12)
plot(tsales, type="o", pch=19)
start(tsales)
end(tsales)
frequency(tsales)
```

*对对象取子集*

```{r}
tsales.subset=window(tsales, start=c(2003, 5), end=c(2004, 6))
tsales.subset
```

### 通过 ma() function from [forecast](https://cran.r-project.org/web/packages/forecast/) package 简单移动平均进行平滑处理  

```{r warning=FALSE, message=FALSE}
library(forecast)
```
```{r echo=TRUE}
opar=par(no.readonly = TRUE)
par(mfrow=c(2,2))
ylim=c(min(Nile), max(Nile))
plot(Nile, main="Raw time series")
plot(ma(Nile, 3), main="Simple Moving Averages (k=3)", ylim=ylim)
plot(ma(Nile, 7), main="Simple Moving Averages (k=7)", ylim=ylim)
plot(ma(Nile, 15), main="Simple Moving Averages (k=15)", ylim=ylim)
par(opar)
```

###通过 stl() function 进行季节性分解  
- trend component: 捕捉长期变化  
- seasonal component: 捕捉周期性变化  
- error component: 捕捉到不能被趋势或季节效应解释的变化  

#### An example: AirPassengers  
序列的波动随着整体水平的增长而增长, 相乘模型更适合  
*stl() 只能处理相加模型, 因而通过对数变换转换成相加模型*

```{r}
plot(AirPassengers)
lAirPassengers=log(AirPassengers)
plot(lAirPassengers, ylab="log(AirPassengers)")
fit=stl(lAirPassengers, s.window = "period")
plot(fit, main="季节性分解图, 灰色长条表示量级")
```

下列code给出观测值中趋势, 季节以及随机项的具体组成, 及其原始尺度

```{r eval=FALSE}
fit$time.series
exp(fit$time.series)
```

季节分解可视化

```{r warning=FALSE, message=FALSE}
monthplot(AirPassengers, xlab="", ylab="")
seasonplot(AirPassengers, year.labels = "TRUE", main="")
```

